Code Appendix

### 2022-12-12 Project_Final_Code.Rmd
FINAL code for project

---
title: "Final Project Code"
author: "Emily, Julian, Jacob, and Aristo"
date: '2022-11-20'
output: 
  html_document:
    df_print: paged
    toc: true
    code_download: true
    theme: paper
---

>>>>

---
title: "Code Appendix"
author: "Emily, Julian, Jacob, and Aristo"
date: '2022-12-12'
output: 
  html_document:
    df_print: paged
    toc: true
    code_download: true
    theme: paper
---
